Decompositions of congruence subgroups of Chevalley groups

### 2015-10-17 paper.tex
Fixed definition of \mathcal{Z}(S)

Here for a subset of roots $S\subseteq\Phi$ we denote by $\mathcal{Z}(S)$ the set
\[ \mathcal{Z}(S) = \{ z_\alpha(s, \xi) \mid s\in I, \ \xi \in R, \ \alpha \in \Phi\}.\]

The following recent result of A.~Stepanov served as a starting point for the present paper.
The notation for the subgroups involved in the statements of our results below is introduced properly in section~\ref{sec:prelim}.
\begin{prop}[{\cite[Theorem~3.4]{S}}] \label{prop:Stepanov}
Let $\Phi$ be a reduced irreducible root system of rank $\geq 2$, let $S \subset \Phi$ be any parabolic subset of roots.
Let $\Sigma_S$ be the special part of $S$, then $\E(\Phi, R, I)$ is generated as an abstract group by the set $\mathcal{Z}(\Sigma_S)$, where
$$\mathcal{Z}(\Sigma) = \mathcal{X} \cup \{ z_\alpha(s, \xi) \mid s \in I, \ \xi \in R, \ \alpha\in \Sigma \}.$$ \end{prop}

>>>>

Here for a subset of roots $S\subseteq\Phi$ we denote by $\mathcal{Z}(S)$ the set
\[ \mathcal{Z}(S) =  \mathcal{X} \cup \{ z_\alpha(s, \xi) \mid s\in I, \ \xi \in R, \ \alpha \in S\}.\]

The following recent result of A.~Stepanov served as a starting point for the present paper.
The notation for the subgroups involved in the statements of our results below is introduced properly in section~\ref{sec:prelim}.
\begin{prop}[{\cite[Theorem~3.4]{S}}] \label{prop:Stepanov}
Let $\Phi$ be a reduced irreducible root system of rank $\geq 2$, let $S \subset \Phi$ be any parabolic subset of roots.
Let $\Sigma_S$ be the special part of $S$, then $\E(\Phi, R, I)$ is generated as an abstract group by the set $\mathcal{Z}(\Sigma_S)$. \end{prop}
